Vulnerability Analysis of Container Images in Neuroimaging field

### 2020-01-17 paper.tex

\title{Risks of Running Vulnerable Container Images for Data Analysis on HPC
Clusters}

@@

As we are taking a particular use case of containers from
neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
in this section we summarize the data and tools 
that are used in CONP. CONP is a national platform for sharing neuroscience
research data and aims at creating an interactive interface for neuroscientists and
clinical neuroscience. The main goal of the CONP platform is to store, process, and
distribute massive amounts of data produced by modern neuroscience.
Here, we summarize all the resources that are
used by CONP to function.

@@

Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2016singularity}. Once Singularity image
is created, it is hashed by using SHA256 hashing. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.

Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.

@@

Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root, and is remotely controlled through a
UNIX socket. It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc..
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. As Docker users directly interact with the
Docker daemon, it is possible to force Docker daemon to escalate privileges.
If a user gets \textit{root} privileges, it introduces unthinkable security risks
for multi-tenant shared enviornments. Due to this reason, Docker is not
supported by HPC environments. However, Docker containers can be imported into
Singularity and then used on HPC clusters.

@@

A container image is a package that contains the application along with its
required dependencies and libraries.
Nowadays, two most popular containerization tools used are Docker and Singularity.
Both have different image format. Below we provide description of both image
formats.

@@

Docker images are organized as a series of layers stacked on top of each
other and identified by unique layer identifiers. If a layer is reused
in different images it will
have the same id across images. Each layer consists of a filesystem diff
with respect to the layer below. DockerHub uses gzip compression for
transferring layers. There are two ways to create a Docker image. The
first is to use an existing Docker image as a base image and then build a
new image from that one, by making changes in the filesystem, which is
saved as a new layer of the Docker image. The second way is to build a new
Docker image from scratch. Docker supports several different storage drivers.
\textit{Overlay2} is the preferred storage driver used by Docker for all currently
supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
zfs, and vfs}

@@

Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. However, it also supports two other formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.

@@

BIDS and Boutiques images that we took for our experiment have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine.
Some Ubuntu distributions that are present inside images are old enough
that Ubuntu has stopped providing support such as 14.04 Long Term Support (LTS), 17.04, and 17.10. These
distributions have reached End Of Life (EOL). They are still used in images, and
as there are no options of getting updates due to EOL, it results in vulnerable images.
However, Extended Security Maintenance 
(ESM) can be requested for Ubuntu 14.04 but it is not feasible to use inside images.

@@

If there exist vulnerabilities in the container image, then there are two ways
to proceed, either not to run that image at all, or run only after updating the
image. Updating the image involves updating all software packages that are
inside that image. However, this option effects the reproducibility
of the image, which means that the image cannot be used to verify research
findings of other scientists. An alternative approach can be to trim unnecessary
packages from images, which in turn reduces the number of vulnerabilities
present in images.

@@

Out of the various container image scanning tools available to scan Docker images,
we selected Anchore
and Vuls because these are the most mature scanning tools. To scan Singularity images
we use Stools, which is specially designed for Singularity images. This tool internally uses
ClairScanner tool so we included ClairScanner also in our experiements to compare
performance of both the tools.

@@

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
Anchore is a set of tools, which users can
employ for scanning container images and applying custom policies to them.
It provides visibility and transparency of the container environment.
Anchore offers services in two ways: Anchore Engine and Anchore Engine
Command Line Interface (CLI). Anchore Engine is available as a Docker
image, which is available on Docker Hub. Anchore Engine CLI provides
command line interface in addition to Anchore Engine REST API. It can be
installed directly on the host and used to inspect images.
Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.

\subsubsection{Vuls}

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
It is an agentless vulnerability scanner and uses various
vulnerability databases. Using dynamic scanning technique, it offers
remote and local scan. Remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer fast scan, fast root scan,
and deep scan.
Fast scan is performed without root privileges, whereas fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these pro-
cesses. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. Deep scan uses
root privileges for scanning, and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.

@@

CoreOS originally created Clair, which is a static vulnerability scanner for containers which
currently support App Container (appc) and Docker~\cite{coreos_2019}. The main goal of the
tool is to provide a transparent look of container’s security. Consequently, it is
named as Clair, simply implying clear. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert systems that there is an updation in the vulnerability metadata. Quay
registery uses Clair internally as the security engine. However, Clair does not 
provide facility of comparing
the vulnerability list of a particular image against a whitelist~\cite{arminc_2019}. So to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in whitelist.

@@

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's ClairScanner with the Continuous Integration (Travis and
Circle) for scanning Singularity images for vulnerabilities.
Initially, ClairScanner was intented to scan Docker Containers. This tool does not fit well
to scan Singularity images because of the different image formats. Docker layers
consist of layers, whereas Singluarity images consist of a single binary file.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a ClairScanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

Table~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely
Anchore, Clair, and Vuls. These scanners are taking vulnerability feed from different sources. For
example for Ubuntu OS distribution, Anchore refers to Ubuntu launchpad database, Clair refers to
Ubuntu CVE Tracker, whereas Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
The interesting point in the table is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls. Also, it is interesting to note that
Anchore reports more number of vulnerabilities than Clair and Vuls for all images except that have Centos OS.
Additionally, we notice that Alpine and Centos OS distributions have less number of vulnerabilities as
compared to Ubuntu and Debian.

\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c},
        table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table}

\begin{figure}[!htb]
        {\includegraphics[width=\columnwidth]
        {Figures/vulngraph.png}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure}

@@

The number and type of vulnerabilities reported by these scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.
According to our investigation of these results precisely, below are some of the reasons of
getting different results from these scanners. These reasons include bugs in scanner's logic,
some scanners ignoring vulnerabilities in a particular package, referring to different databases,
how frequently they are updating their database, etc,. We have explained these differences below in detail
and have provided an example with each reason to make it clear.

\subsection{V-C}

V-C represents extra vulnerabilities that are shown by Vuls than Clair.
So the next question is why they are not shown by Clair then. 
Below are some reasons to answer that question:

\begin{enumerate}

\item\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
affecting particular Ubuntu release that is present inside the image. The reason why its not affecting 
that release is also mentioned. For example, one reason can be that code which is creating issue is not 
present in that release etc. In other words, we can say that these are false positives by Vuls.
For example CVE-2015-2305 is not affecting package cups in Trusty.

\item\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life 
but does not exist (status as “DNE”) in Ubuntu 14.04 ESM release. As Clair is only referring Ubuntu 14.04 ESM 
release it do not detect these vulnerabilities. For example CVE-2017-9994.

\item\textbf{Not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.

\item\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
is present in package cairo in Xenial release and it is not detected by Clair.
\end{enumerate}

\subsection{C-V}

C-V represents extra vulnerabilities that are shown by Clair than Vuls. Following are the reasons to explain that:

\begin{enumerate}
\item \textbf{False positives by Clair-}These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274.
\item\textbf{False Negatives by Vuls-} For example CVE-2019-5094.
\end{enumerate}

\subsection{A-C}

A-C represents extra vulnerabilities shown by Anchore than Clair. Below are the reasons:
\begin{enumerate}
	\item\textbf{Linux Package-} Clair is not detecting all vulnerabilities in the source “Linux” package. 
		For example CVE-2019-9506.
	\item\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it 
		reached end-of-life but does not exist (DNE) in ESM release. As Clair is only referring 
		Ubuntu 14.04 ESM release it do not detect it. For example CVE-2017-994.
	\item\textbf{Database difference-} Clair is using a Docker image for database. So it is not updated everyday. 
		When I scanned images I used the latest available container. For example CVE-2019-5094 was not 
		updated in Clair container that time.
	\item\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example 
		CVE-2016-9082 is present in package cairo in Xenial release and it is not detected by Clair.
\end{enumerate}

\subsection{C-A}
C-A represents the vulnerabilities that are not detected by Anchore. Below are the reasons:
\begin{enumerate}

	\item\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when package’s version have epoch 
		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.
	\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.
	\item\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
		so Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve 
		prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not. But this 
		vulnerability is present in Ubuntu 14.04 ESM release so Clair is reporting that. For example CVE-2019-9924.
\end{enumerate}

\subsection{A-V}

A-V represents the vulnerabilities that are detected by Anchore but not detected by Vuls. Below are the reasons 
of these differences:
\begin{enumerate}

	\item\textbf{Linux Package-} Vuls is not detecting all vulnerabilities in the source “Linux” package. 
		For example CVE-2019-9506
	\item\textbf{False Negatives by Vuls-} Vuls is missing some of the vulnerabilities that it should detect. 
		For example CVE-2019-5094
\end{enumerate}

\subsection{V-A}
V-A represents the vulnerabilities that are detected by Vuls but not detected by Anchore. Below are the reasons:
\begin{enumerate}
\item\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are not detected 
	by Anchore. This bug gets triggered when package’s version have epoch (1:3.3.9-1ubuntu2.3)  in it. 
		For example CVE-2018-1125 in procps package
\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to which it is not 
	able to detect some vulnerabilities. Due to this bug Anchore does not detect vulnerabilities which 
		have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. But these vulnerabilities 
		are detected by Vuls in Ubuntu 14.04 LTS. For example CVE-2019-13565 in Ubuntu 14.04
\item\textbf{With status as “Not-affected”-}  It means these vulnerabilities are affecting Ubuntu but they are not 
	affecting particular Ubuntu release that is present inside the image. The reason why its not affecting that 
		release is also mentioned. For example, one reason can be that code which is creating issue is not 
		present in that release etc. For example CVE-2015-2305 is not affecting package cups in Trusty.
\item\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753
	\end{enumerate}

>>>>

\title{Vulnerability Analysis of Container Images in Neuroimaging field}

@@

\begin{comment}
As we are taking a particular use case of containers from
neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
in this section we summarize the data and tools 
that are used in CONP. CONP is a national platform for sharing neuroscience
research data and aims at creating an interactive interface for neuroscientists and
clinical neuroscience. The main goal of the CONP platform is to store, process, and
distribute massive amounts of data produced by modern neuroscience.
Here, we summarize all the resources that are
used by CONP to function.
\end{comment}

@@

Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2016singularity}. Once Singularity image
is created, it is hashed by using SHA256 hashing. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.

@@

Docker runs a software, \textit{Docker daemon}, on the host machine.
Docker daemon runs as root, and is remotely controlled through a
UNIX socket. It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc..
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. As Docker users directly interact with the
Docker daemon, it is possible to force Docker daemon to escalate privileges.
If a user gets \textit{root} privileges, it introduces unthinkable security risks
for multi-tenant shared enviornments. Due to this reason, Docker is not
supported by HPC environments. However, Docker images can be imported into
Singularity and then used on HPC clusters.

@@

A container image is a package that contains the application along with its
required dependencies and libraries.
Both, Docker and Singularity, have different image format. Below we provide description of both image
formats.

@@

Docker images are organized as a series of layers stacked on top of each
other and identified by unique layer identifiers. If a layer is reused
in different images it will
have the same id across images. Each layer consists of a filesystem diff
with respect to the layer below. DockerHub uses gzip compression for
transferring layers. \begin{comment}There are two ways to create a Docker image. The
first is to use an existing Docker image as a base image and then build a
new image from that one, by making changes in the filesystem, which is
saved as a new layer of the Docker image. The second way is to build a new
Docker image from scratch.\end{comment} Docker supports several different storage drivers.
\textit{Overlay2} is the preferred storage driver used by Docker for all currently
supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
zfs, and vfs}

@@

Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. It is read-only file system in Linux, which uses compression for files,
inodes, and directories. However, Singularity also supports two other 
formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.

@@

BIDS app and Boutiques images that we took for our experiment have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. In case of Ubuntu, release
can be of two types i.e regular or LTS(Long Term Support) release.
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life(EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance(ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases.

Some Ubuntu distributions that are present inside images have already reached EOL such as 14.04 Long Term Support (LTS),
17.04, and 17.10. However, Ubuntu is providing ESM support for Ubuntu 14.04. The images in our experiment have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
in false positives and false negatives.
Also, if these releases with EOL are used in images, there are no chances of getting updates, hence
resulting in vulnerable images. Additionally, even if ESM release is present for some EOL release it is
not feasible to use inside images.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks
package manager present inside the image and then according to that it
updates the image. However, this option effects the reproducibility
of the image, which means that the image cannot be used to verify research
findings of other scientists.

@@

Out of the various container image scanning tools available to scan Docker images,
we selected Anchore~\cite{github_2019}
and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
we use Stools, which is specially designed for Singularity images. This tool internally uses
Clair Scanner tool so we included ClairScanner also in our experiements to compare
performance of both the tools. So total there are three scanners for Docker images
and one scanner for Singularity images.

@@

Anchore is an end-to-end, open-source container security platform. Anchore
is a static
scanning tool that analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
Anchore is a set of tools, which users can
employ for scanning container images and applying custom policies to them.
It provides visibility and transparency of the container environment.
It offers services in two ways: Anchore Engine and Anchore Engine
Command Line Interface (CLI). Anchore Engine is available as a Docker
image, which is available on Docker Hub. Anchore Engine CLI provides
command line interface in addition to Anchore Engine REST API. It can be
installed directly on the host and used to inspect images.
Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get vulnerability feed of various OS distribution, Anchore refers to
different sources. For example Ubuntu launchpad database is used for Ubuntu. 
\subsubsection{Vuls}

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
It is an agentless vulnerability scanner and uses various
vulnerability databases. Using dynamic scanning technique, it offers
remote and local scan. Remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer fast scan, fast root scan,
and deep scan.
Fast scan is performed without root privileges, whereas fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these pro-
cesses. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. Deep scan uses
root privileges for scanning, and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
meaning that images with these distributions are impossible to scan with Vuls.

@@

CoreOS originally created Clair, which is a static vulnerability scanner for containers which
currently support App Container (appc) and Docker~\cite{coreos_2019}. The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert systems that there is an updation in the vulnerability metadata. Quay
registery uses Clair internally as the security engine. However, Clair does not 
provide facility of comparing
the vulnerability list of a particular image against a whitelist~\cite{arminc_2019}. So to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in whitelist.
Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.

@@

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with the Continuous Integration (Travis and
Circle) for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intented to scan Docker Containers. This tool does not fit well
to scan Singularity images because of the different image formats. Docker layers
consist of layers, whereas Singluarity images consist of a single binary file.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

Figure~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely Anchore,
Clair scanner and Vuls. Venn Diagram in Figure~\cite{fig:venn} summarizes this table. It is interesting to note that
Anchore reports 4453 different vulnerabilities, which is way more than both Clair and Vuls.
Additionally, we notice that Alpine and Centos OS distributions have less number of vulnerabilities as
compared to Ubuntu and Debian.
\begin{table}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\columnwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c},
        table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table}

\begin{figure}[!htb]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.png}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

\begin{figure}[!htb]
        {\includegraphics[scale=2,width=\columnwidth]
        {Figures/vulngraph.png}}
        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
      \end{figure}

@@

The number and type of vulnerabilities reported by these scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.
According to our investigation of these results precisely, below are some of the reasons of
getting different results from these scanners. These reasons include bugs in scanners,
some scanners ignoring vulnerabilities in a particular package, referring to different databases,
how frequently they are updating their databases, etc,. We have explained these differences below in detail
and have provided an example with each reason to make it clear.

Venn Diagram~\cite{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
by Vuls and Clair. Out of this 4443 vulnerabilities are present in linux-kernel-headers. These are ignored by
both Clair and Vuls.

\textbf{Linux Package-} Clair and Vuls are ignoring all vulnerabilities in the "Linux” package
which is linux-kernel-headers. 4443 out of 4453 vulnerabilities difference is due to linux-kernel-headers.
For example CVE-2019-9506 is not detected by.

\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
affecting particular Ubuntu release that is present inside the image. The reason why its not affecting 
that release is also mentioned. For example, one reason can be that code which is creating issue is not 
present in that release etc. In other words, we can say that these are false positives by Vuls.
For example CVE-2015-2305 is not affecting package cups in Trusty.

\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life 
but does not exist (status as “DNE”) in Ubuntu 14.04 ESM release. As Clair is only referring Ubuntu 14.04 ESM 
release it do not detect these vulnerabilities. For example CVE-2017-9994.

\textbf{Not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.

\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
is present in package cairo in Xenial release and it is not detected by Clair.

\textbf{False positives by Clair-}These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274.

\textbf{Database difference-} Clair is using a Docker image for database. So it is not updated everyday. 
		When I scanned images I used the latest available container. For example CVE-2019-5094 was not 
		updated in Clair container that time.

\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when package’s version have epoch 
		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.

\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
		so Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve 
		prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not. But this 
		vulnerability is present in Ubuntu 14.04 ESM release so Clair is reporting that. For example CVE-2019-9924.

\textbf{False Negatives by Vuls-} Vuls is missing some of the vulnerabilities that it should detect. 
		For example CVE-2019-5094

\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753
